Problem Set 2 (Answers)

### 2019-09-27 static/homeworks/02-problem-set-answers.Rmd
Fix n -> n-1 in problem set 2 answers!

1. Find the mean of $X$, $(\bar{X})$
2. Subtract the mean from each value of $X$ in the data, to get deviations, $(x_i-\bar{X})$
3. Square the deviations to ensure they are all positive, $(x_i-\bar{X})^2$
4. Take the average of the squared deviations: add them all up and divide by $n-1$, $\frac{1}{n}\displaystyle \sum^n_{i=1} (x_i-\bar{X})^2$
5. What you have in step 4 is variance (measured in units of $X^2)$, square root to get standard deviation (measured in original units of $X$): $\sqrt{\frac{1}{n}\displaystyle \sum^n_{i=1} (x_i-\bar{X})^2}$

>>>>

1. Find the mean of $X$, $(\bar{X})$
2. Subtract the mean from each value of $X$ in the data, to get deviations, $(x_i-\bar{X})$
3. Square the deviations to ensure they are all positive, $(x_i-\bar{X})^2$
4. Take the average of the squared deviations: add them all up and divide by $n-1$, $\frac{1}{n-1}\displaystyle \sum^n_{i=1} (x_i-\bar{X})^2$
5. What you have in step 4 is variance (measured in units of $X^2)$, square root to get standard deviation (measured in original units of $X$): $\sqrt{\frac{1}{n-1}\displaystyle \sum^n_{i=1} (x_i-\bar{X})^2}$
